---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data  
Code shown below read the csv file into R data frame.  
```{r}
activity.raw <- read.csv("./data/activity.csv", na.strings = "NA")
activity.dated <- activity.raw
```
To transform the date column into the date data type, the following code is used.
```{r}
activity.dated$date <- as.Date(activity.dated[,2], format = "%Y-%m-%d")
```


## What is mean total number of steps taken per day?
First, calculate the total steps taken each day:
```{r}
day.total <- tapply(activity.raw$steps, activity.raw$date, sum, na.rm = TRUE)
```
Here is the histogram for the calculated results:
```{r histogram, fig.height=4}
hist(day.total, main = "Frequency for Total Number of Steps Taken Each Day",
     xlab = "Total Number of Steps")
```


## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
